A finite-state morphological transducer for Kyrgyz

### 2012-03-14 paper/paper.tex
7.2 fixes

To calculate precision and recall, it was necessary to create a hand-verified list of surface forms and their analyses. We extracted 1,000 unique surface forms at random from the RFERL corpus, and checked that they were valid words in Kyrgyz and correctly spelt. Where a word was incorrectly spelt, it was discarded and a new random word selected.

>>>>

Precision and recall are measures of the average accuracy of analyses provided by a morphological transducer.  Precision represents the number of the analyses given for a form that are correct.  Recall is the percentage of analyses that are deemed correct for a form (by comparing against a gold standard) that are provided by the transducer.

To calculate precision and recall, it was necessary to create a hand-verified list of surface forms and their analyses. We extracted 1,000 unique surface forms at random from the RFERL corpus, and checked that they were valid words in Kyrgyz and correctly spelt.  Where a word was incorrectly spelt or deemed not to be a form used in Kyrgyz, it was discarded and a new random word selected.
